### 2020-01-20 manuscript/bef_stability/manuscript.Rmd
Improve plots + latex path analysis

knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

@@

stab_div_troph <- temporal_network_metrics %>%
  dplyr::select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  dplyr::select(station, troph_group, biomass_stab, richness_med)
```

@@

$$
S_i = \beta_0 + \beta_Rx_{Ri} + \epsilon_{ij}
$$

```{r mod-div-total}
ctrl <- lmeControl(opt='optim')
stab_div_mod <- lme(data = sem_data,
  fixed = log_stab ~ log_rich,
  random = ~ 1 + log_rich | basin,
  control = ctrl 
)
#stab_div_colin <- car::vif(stab_div_mod)
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke")
```

```{r predict}
pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    basin = group
  )

@@

```{r s-div, fig.dim = c(10,5)}
label_rsq <- "paste(
  \"Conditional italic(R) ^ 2 == \", round(stab_div_sum$Conditional, 2),
  \", Marginal italic(R) ^ 2 == \", round(stab_div_sum$Marginal, 2))"
# Plot left  
p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_stab))+
  geom_point() +
  #scale_x_log10() + scale_y_log10() +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .5) +
  annotate("text", x = 1.0, y = .8, label = paste(
  " Marg. R^2 = ", round(stab_div_sum$Marginal, 2),
  ", Cond. R^2 = ", round(stab_div_sum$Conditional, 2)
  )
    )

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = richness_med, y = biomass_stab, color = troph_group)) +
  geom_point() +
  geom_smooth(method = "lm" ) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  scale_x_log10() + scale_y_log10() +
  labs(x = "Average species richness", y = "Biomass stability")

plot_grid(p_stab_div, p_stab_div_troph, ncol = 2, rel_widths = c(.4, .6))
```

@@

- Community structure: 
  - Richness decreases synchrony but increases CV
  - Trophic level increases synchrony but decreases CV
  - Betadiv increases CV

- Stability component:
  - CV is the main driver of stability

>>>>

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

@@

stab_div_troph <- temporal_network_metrics %>%
  dplyr::select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group),
    log_rich = log10(richness_med),
    log_bm = log10(biomass_med),
    log_stab = log10(biomass_stab)) %>%
  dplyr::select(station, troph_group, biomass_stab, richness_med, log_rich, log_stab, log_bm, biomass_med) %>%
  dplyr::left_join(st_basin, by = "station")
```

@@

$$
\Log_{10}(S_i) = \beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij}
$$

$$
S_i = 10^(\beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij})
$$

$$
S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) * 10^(\epsilon_{ij})
$$

with $i$ being the station $i$.

```{r mod-div-total}
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optim'))
stab_div_mod <- lmer(data = sem_data,
  #control = ctrl_lmer,
  formula = log_stab ~ log_rich + (1 | basin)
)
stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
#stab_div_colin <- car::vif(stab_div_mod) not use if one response
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    basin = group
  )

#
bm_div_mod <- lme(data = sem_data,
  fixed = log_bm ~ log_rich,
  random = ~ 1 + log_rich | basin,
  control = ctrl 
)
bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(bm_div_mod, terms = c("log_rich"), type = "fe")
#plot(pred, add.data = TRUE)
bm_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich = x,
    basin = group
  )
```

```{r mod-div-troph}
stab_troph_mod <- lme(data = na.omit(stab_div_troph),
  fixed = log_stab ~ log_rich + troph_group + log_rich:troph_group,
  random = ~ 1 | basin,
  control = ctrl
)

stab_troph_colin <- car::vif(stab_troph_mod)
stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich = x,
    troph_group = group
  )

# Productivity and troph group

bm_troph_mod <- lme(data = na.omit(stab_div_troph),
  fixed = log_bm ~ log_rich * troph_group,
  random = ~ 1 + log_rich * troph_group | basin,
  control = ctrl 
)

bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
bm_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich = x,
    troph_group = group
  )
```

@@

```{r p-s-div}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
filter(stab_div_troph, log_rich < 0)
# Plot left  
p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich) +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich, y = log_stab, color = troph_group)) +
  geom_point() +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  ylim(lim_log_stab) +
  xlim(lim_log_rich) +
  geom_line(data = stab_troph_pred) +
  geom_ribbon(data = stab_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)")

p_stab <- plot_grid(p_stab_div, p_stab_div_troph, ncol = 2, rel_widths = c(.4, .6))
```

```{r p-p-div}
lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm")

p_bm_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_bm))+
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich) +
  labs(x = "Median species richness (Log 10)", y = " Total biomass(Log 10)") +
  geom_line(data = bm_div_pred) +
  geom_ribbon(data = bm_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = 5, label = make_label_rsq(rsq = bm_div_sum),
    parse = TRUE)

p_bm_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich, y = log_bm, color = troph_group)) +
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  geom_line(data = bm_troph_pred) +
  geom_ribbon(data = bm_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = 5, label = make_label_rsq(rsq = bm_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = "Median species richness (Log 10)", y = "Total biomass (Log 10)")

p_bm <- plot_grid(p_bm_div, p_bm_div_troph, ncol = 2, rel_widths = c(.4, .6))
```

```{r psbm, fig.dim = c(10,5)}
plot_grid(p_stab, p_bm, ncol = 1)
```

- Stability:
  - decreases with richness
  - is higher for higher trophic group
  - increases and decreases with richness for the lower and higher trophic group
    respectively

- richness on stab:
  - globally negative
  -

@@

- Stability:
  - Stability component:
    - CV is the main driver of stability:
  - Community structure: 
    - Richness decreases synchrony but increases CV
    - Trophic level increases synchrony but decreases CV
    - Betadiv increases CV
  - Habitat/Env:
    - very weak to no direct effect on stability
      - direct: CV_sp dec with increasing RC3, cad enrichment and flow_cv decrease.  
    - indirectly affect stability by modulating community structure

- Total biomass:
  - Community structure:
    - Richness increased total biomass / had the bigger effect
    - Even community deceased total biomass
    - Species turnover decreased total biomass  
    - Connectance increased biomass
  - Habitat/Env:
    - very weak to no direct effect on total biomass 
    - Effect of environment is thus mediated by the community structure

- Main outcome

- Latex:
  - csv:
    - https://tex.stackexchange.com/questions/178904/use-datatool-to-read-a-row-from-a-csv-file-then-use-the-variables-in-the-docume
    - https://tex.stackexchange.com/questions/40901/datatool-getting-a-specific-value-given-the-value-of-another-column
  - path:

### 2020-01-20 report/sem_tex/stab_sem.tex
Improve plots + latex path analysis

    %bmility
    \node [place] (bm)  [below of=rich] {Total biomass};

    \path 
	(rc3) edge node[anchor=south,above]{$SC_n=0$} (piel)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (rich)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (beta)
	(rc3) edge (troph)
	(rc3) edge (c)
	(rc3) edge (bm)

	(rc2) edge (piel)
	(rc2) edge (rich)
	(rc2) edge (beta)
	(rc2) edge (troph)
	(rc2) edge (c)
	(rc2) edge (bm)

	(rc1) edge (piel)
	(rc1) edge (rich)
	(rc1) edge (beta)
	(rc1) edge (troph)
	(rc1) edge (c)
	(rc1) edge (bm)

	(rc4) edge (piel)
	(rc4) edge (rich)
	(rc4) edge (beta)
	(rc4) edge (troph)
	(rc4) edge (c)
	(rc4) edge (bm)

	(rc5) edge (piel)
	(rc5) edge (rich)
	(rc5) edge (beta)
	(rc5) edge (troph)
	(rc5) edge (c)
	(rc5) edge (bm)
	;

    \path 
	(piel)  edge (bm)
	(rich)  edge (bm)
	(beta)  edge (bm)
	(troph) edge (bm)
	(c) edge (bm)
	(bm) edge (bm)
	;

>>>>

    %Stability
    \node [place] (cv) [below left of=rich] {$CV_{sp}$};
    \node [place] (sync) [below right of=rich] {Synchrony};
    \node [place] (stab)  [below left of=sync] {Biomass stability};

    \path 
	(rc3) edge node[anchor=south,above]{$SC_n=0$} (piel)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (rich)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (beta)
	(rc3) edge (troph)
	(rc3) edge (c)
	(rc3) edge (sync)
	(rc3) edge (cv)

	(rc2) edge (piel)
	(rc2) edge (rich)
	(rc2) edge (beta)
	(rc2) edge (troph)
	(rc2) edge (c)
	(rc2) edge (sync)
	(rc2) edge (cv)

	(rc1) edge (piel)
	(rc1) edge (rich)
	(rc1) edge (beta)
	(rc1) edge (troph)
	(rc1) edge (c)
	(rc1) edge (sync)
	(rc1) edge (cv)

	(rc4) edge (piel)
	(rc4) edge (rich)
	(rc4) edge (beta)
	(rc4) edge (troph)
	(rc4) edge (c)
	(rc4) edge (sync)
	(rc4) edge (cv)

	(rc5) edge (piel)
	(rc5) edge (rich)
	(rc5) edge (beta)
	(rc5) edge (troph)
	(rc5) edge (c)
	(rc5) edge (sync)
	(rc5) edge (cv)
	;

    \path 
	(piel)  edge (sync)
	(piel)  edge (cv)
	(rich)  edge (sync)
	(rich)  edge (cv)
	(beta)  edge (sync)
	(beta)  edge (cv)
	(troph) edge (sync)
	(troph) edge (cv)
	(c) edge (sync)
	(c) edge (cv)
	(cv) edge (stab)
	(sync) edge (stab)
	;

### 2020-01-20 report/sem_tex/theoric_sem.tex
Improve plots + latex path analysis

\begin{tikzpicture}[node distance=4cm,->,>=stealth',bend angle=45,auto]

@@

    % Evt 
    \node [place] (rc3)  {RC3};
    \node [place] (rc2) [left of=rc3] {RC2};
    \node [place] (rc1) [left of=rc2] {RC1};
    \node [place] (rc4) [right of=rc3] {RC4};
    \node [place] (rc5) [right of=rc4] {RC5};

   %Community structure 
    \node [place] (rich) [below of=rc3] {Species richness};
    \node [place] (piel) [left of=rich] {Pielou};
    \node [place] (beta)  [left of=piel] {$\beta$-diversity};
    \node [place] (troph) [right of=rich] {Trophic level};
    \node [place] (c)  [right of=troph] {Connectance};

    %Stability
    \node [place] (cv) [below left of=rich] {$CV_{sp}$};
    \node [place] (sync) [below right of=rich] {Synchrony};
    \node [place] (stab)  [below left of=sync] {Biomass stability};

    \path 
	(rc3) edge node[anchor=south,above]{$SC_n=0$} (piel)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (rich)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (beta)
	(rc3) edge (troph)
	(rc3) edge (c)
	(rc3) edge (sync)
	(rc3) edge (cv)

	(rc2) edge (piel)
	(rc2) edge (rich)
	(rc2) edge (beta)
	(rc2) edge (troph)
	(rc2) edge (c)
	(rc2) edge (sync)
	(rc2) edge (cv)

	(rc1) edge (piel)
	(rc1) edge (rich)
	(rc1) edge (beta)
	(rc1) edge (troph)
	(rc1) edge (c)
	(rc1) edge (sync)
	(rc1) edge (cv)

	(rc4) edge (piel)
	(rc4) edge (rich)
	(rc4) edge (beta)
	(rc4) edge (troph)
	(rc4) edge (c)
	(rc4) edge (sync)
	(rc4) edge (cv)

	(rc5) edge (piel)
	(rc5) edge (rich)
	(rc5) edge (beta)
	(rc5) edge (troph)
	(rc5) edge (c)
	(rc5) edge (sync)
	(rc5) edge (cv)
	;

    \path 
	(piel)  edge (sync)
	(piel)  edge (cv)
	(rich)  edge (sync)
	(rich)  edge (cv)
	(beta)  edge (sync)
	(beta)  edge (cv)
	(troph) edge (sync)
	(troph) edge (cv)
	(c) edge (sync)
	(c) edge (cv)
	(cv) edge (stab)
	(sync) edge (stab)
	;

\end{tikzpicture}

>>>>

\begin{tikzpicture}[node distance=3.3cm,>=stealth',bend angle=45,auto]

@@

  \begin{scope}
    % First net
    \node [place] (evt) {Environment};
    \node [place] (com) [below of=evt] {Community structure}
      edge [pre]                            (evt);
    \node [place] (stab)  [below of=com] {Biomass\\\
	stability}
      edge [pre]                            (com)
      edge [pre, bend left]                            (evt);

  \end{scope}

  \begin{scope}[xshift=6cm]
    % Second net
    \node [place] (evt1) {Environment};
    \node [place] (com1) [below of=evt1] {Community structure}
      edge [pre]                            (evt1);
    \node [place] (bm)  [below of=com1] {Total biomass}
      edge [pre]                            (com1)
      edge [pre, bend right]                (evt1);
  \end{scope}

  \begin{pgfonlayer}{background}
    \filldraw [line width=2cm,join=round,black!10]
      (evt.north  -| stab.east)  rectangle (stab.south  -| stab.west)
      (evt1.north -| bm.east) rectangle (bm.south -| bm.west);
  \end{pgfonlayer}
\end{tikzpicture}
